### 2015-02-17 Docs/getting_started/getting_started.tex

Here we will run the standard {\tt test2} problem (three reacting
bubbles in a plane-parallel stratified atmosphere) on a single
processor.  This test problem was shown in paper~3.

@@

Change directory to {\tt MAESTRO/Exec/TEST\_PROBLEMS/test2/}.    
We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

Note, at the end of the build process, a link will be made in the current
directory to the data
table needed for the equation of state ({\tt extern/EOS/helmeos/helm\_table.dat}).

@@

Each problem requires an input file.  The inputs file (a Fortran
namelist) consists of
lines of the form {\em parameter = value}, where {\em parameter} is
one of the many runtime parameters \maestro\ knows, and {\em value}
overrides the default value for that parameter.  For the {\tt test2}
problem, we will use the inputs file {\tt inputs\_2d}.  An overview of
some of the more common runtime parameters is given
in \S~\ref{sec:gettingstarted:runtime}, and a full list of
all \maestro\ runtime parameters and their default values is given in
Chapter~\ref{ch:runtimeparameters}.

@@

Visualization and analysis are done on the plotfiles.  A number of
in-house and externally developed tools can work
with \boxlib-formatted plotfiles.  An example plot of the {\tt test2}
problem run above is shown in Figure~\ref{fig:gettingstarted:test2}.

\begin{figure}[t]
\centering
\includegraphics[width=3in]{\gsfigpath/plt00133_tfromp}
\caption[Visualization of {\tt test2} output]{\label{fig:gettingstarted:test2} Visualization of the
final output of the {\tt test2} problem showing the temperature
field (as derived from the pressure).  This plot was done with
the {\tt AmrPostprocessing} tools.}
\end{figure}

@@

\item {\tt test2} \\[-3mm]

{\tt test2} places 3 hots spots in a plane-parallel atmosphere.
Burning makes these bubbles buoyant, and then roll up.  This problem was
used in \cite{lowMach3} to compare with compressible solvers.

>>>>

Here we will run the standard {\tt reacting\_bubble} problem (three
reacting bubbles in a plane-parallel stratified atmosphere) on a
single processor\footnote{In earlier versions of \maestro\ this
problem was called {\tt test2}}.  This test problem was shown in
paper~3.

@@

Change directory to {\tt MAESTRO/Exec/TEST\_PROBLEMS/reacting\_bubble/}.    
We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

Note, at the end of the build process, a link will be made in the
current directory to the data table needed for the equation of state
({\tt Microphysics/EOS/helmeos/helm\_table.dat}).

@@

Each problem requires an input file.  The inputs file (a Fortran
namelist) consists of
lines of the form {\em parameter = value}, where {\em parameter} is
one of the many runtime parameters \maestro\ knows, and {\em value}
overrides the default value for that parameter.  For the {\tt reacting\_bubble}
problem, we will use the inputs file {\tt inputs\_2d}.  An overview of
some of the more common runtime parameters is given
in \S~\ref{sec:gettingstarted:runtime}, and a full list of
all \maestro\ runtime parameters and their default values is given in
Chapter~\ref{ch:runtimeparameters}.

@@

Visualization and analysis are done on the plotfiles.  A number of
in-house and externally developed tools can work
with \boxlib-formatted plotfiles.  An example plot of the {\tt reacting\_bubble}
problem run above is shown in Figure~\ref{fig:gettingstarted:test2}.

\begin{figure}[t]
\centering
\includegraphics[width=3in]{\gsfigpath/plt00133_tfromp}
\caption[Visualization of {\tt reacting\_bubble} output]{\label{fig:gettingstarted:test2} Visualization of the
final output of the {\tt reacting\_bubble} problem showing the temperature
field (as derived from the pressure).  This plot was done with
the {\tt AmrPostprocessing} tools.}
\end{figure}

@@

\item {\tt reacting\_bubble} \\[-3mm]

{\tt reacting\_bubble} places 3 hots spots in a plane-parallel atmosphere.
Burning makes these bubbles buoyant, and then roll up.  This problem was
used in \cite{lowMach3} to compare with compressible solvers.

### 2015-02-17 Docs/makefiles/makefiles.tex

  This is the module that controls runtime parameters.  This is
  created by the script
  {\tt write\_probin.py} in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_scripts/}.  The
  makefile logic for creating it is in {\tt GMaestro.mak}.  At compile
  time, the problem, main {\tt MAESTRO/}, and {\tt extern/}
  directories are searched for {\tt \_parameter} files.  These files
  are parsed and the {\tt probin.f90} file is output containing the 
  runtime parameters, their default values, and the logic for reading
  and interpreting the inputs file.

@@

  This is generated at compile time {\em only} for the {\tt
  general\_null} network.  The {\tt general\_null} network allows the
  user to define a list of non-reacting species builds the {\tt
  network.f90} based on this list.  The makefile logic for building
  the {\tt network.f90} is in the {\tt GPackage.mak} in {\tt
  extern/networks/general\_null}.  The script {\tt write\_network.py}
  in that directory does the actual parsing of the species file and
  outputs the {\tt network.f90}.

@@

  This variable points to the directory (by default, relative to {\tt Microphysics/EOS/}) of
  the equation of state used for the build.  Choices that work
  with \maestro\ are:
  \begin{itemize}
  \item {\tt extern/EOS/helmeos}
  \item {\tt extern/EOS/gamma\_law\_general}
  \end{itemize}
  To use an EOS contained in a different location, set the variable {\tt EOS\_TOP\_DIR}
  to point to the directory above the alternate EOS directory.

@@

  This variable points to the conductivity routine used for the build
  (by default, relative to {\tt Microphysics/conductivity/}).  Choices
  that work with \maestro\ are: 
  %
  \begin{itemize} 
  \item {\tt extern/conductivity/constant} 
  \item {\tt extern/conductivity/timmes\_stellar} 
  \end{itemize} 
  % 
  If diffusion is not being used for the problem, this should be set
  to {\tt extern/conductivity/constant}.  To use an alternate conductivity
  routine, set the variable {\tt CONDUCTIVITY\_TOP\_DIR} to point
  to the directory above the alternate conductivity directory.

@@

  This variable points to the reaction network used for the build (by
  default, relative to {\tt Microphysics/networks/}).  Several options
  are present in {\tt extern/networks/}.  A network is required even
  if you are not doing reactions, since the network defines the
  species that are advected and interpreted by the equation of state.

  A special choice, {\tt extern/networks/general\_null} is a general
  network that simply defines the properties of one or more species.
  This requires an inputs file, specified by {\tt
  GENERAL\_NET\_INPUTS}.  This inputs file is read at compile-time and
  used to build the {\tt network.f90} file that is compiled into the
  source.

>>>>

  This is the module that controls runtime parameters.  This is
  created by the script
  {\tt write\_probin.py} in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_scripts/}.  The
  makefile logic for creating it is in {\tt GMaestro.mak}.  At compile
  time, the problem, main {\tt MAESTRO/}, and any microphysics
  directories (set from the {\tt EOS\_DIR}, {\tt CONDUCTIVITY\_DIR}, and {\tt NETWORK\_DIR} parameters in the {\tt GNUmakefile}
  are searched for {\tt \_parameter} files.  These files
  are parsed and the {\tt probin.f90} file is output containing the 
  runtime parameters, their default values, and the logic for reading
  and interpreting the inputs file.

@@

  This is generated at compile time {\em only} for the {\tt
  general\_null} network.  The {\tt general\_null} network allows the
  user to define a list of non-reacting species builds the {\tt
  network.f90} based on this list.  The makefile logic for building
  the {\tt network.f90} is in the {\tt GPackage.mak} in {\tt
  Microphysics/networks/general\_null}.  The script {\tt write\_network.py}
  in that directory does the actual parsing of the species file and
  outputs the {\tt network.f90}.

@@

  This variable points to the directory (by default, relative to {\tt
  Microphysics/EOS/}) of the equation of state used for the build.
  Choices that work with \maestro\ are:
  \begin{itemize}
  \item {\tt helmeos}
  \item {\tt gamma\_law\_general}
  \item {\tt multigamma}
  \end{itemize}
  To use an EOS contained in a different location, set the variable {\tt
  EOS\_TOP\_DIR} to point to the directory above the alternate EOS
  directory.

@@

  This variable points to the conductivity routine used for the build
  (by default, relative to {\tt Microphysics/conductivity/}).  Choices
  that work with \maestro\ are: 
  %
  \begin{itemize} 
  \item {\tt constant} 
  \item {\tt timmes\_stellar} 
  \end{itemize} 
  % 
  If diffusion is not being used for the problem, this should be set
  to {\tt constant}.  To use an alternate conductivity
  routine, set the variable {\tt CONDUCTIVITY\_TOP\_DIR} to point
  to the directory above the alternate conductivity directory.

@@

  This variable points to the reaction network used for the build (by
  default, relative to {\tt Microphysics/networks/}).  Several options
  are present in {\tt Microphysics/networks/}.  A network is required even
  if you are not doing reactions, since the network defines the
  species that are advected and interpreted by the equation of state.

  A special choice, {\tt Microphysics/networks/general\_null} is a general
  network that simply defines the properties of one or more species.
  This requires an inputs file, specified by {\tt
  GENERAL\_NET\_INPUTS}.  This inputs file is read at compile-time and
  used to build the {\tt network.f90} file that is compiled into the
  source.
